The Astropy Project

### 2017-10-20 main.tex
Update on Overleaf.

@@

\begin{description}
    \item[Local Earth coordinate frames] In addition to representing celestial
    coordinates, \astropypkg now supports specifying positions on the Earth in
    a number of different geocentric systems with the \texttt{EarthLocation}
    class.
    With this, \astropypkg now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \texttt{Time} class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg or the
    \astropy-affiliated package \package{astroplan}\citep{astroplan_AAS}. 
    \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}
    \inlinecomment{BMS}{better to cite the submitted or soon to be submitted paper}

@@

Q: does it make sense to refer forward to FITS support, even though it is 3.0?

@@

Check when it was added (0.3?). Overview of the supported formats (ASCII,
FITS, votable, HTML, JSViewer/Datatables).

@@

\inlinecomment{SCO}{One subsection per format (if enough new features) ?}

@@

>>>>

\inlinecomment{BMS}{The itemizations below look very weird being boldface under a much less prominent subsection title. would it be nicer in the final version if we leave it as is in the draft?}

@@

\begin{description}
    \item[Local Earth coordinate frames] In addition to representing celestial
    coordinates, \astropypkg now supports specifying positions on the Earth in
    a number of different geocentric systems with the \texttt{EarthLocation}
    class.
    With this, \astropypkg now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \texttt{Time} class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg or the
    \astropy-affiliated package \package{astroplan}\citep{astroplan_AAS}. 
    \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}
    \inlinecomment{BMS}{better to cite the submitted or soon to be submitted paper, I made a placeholder for it.}

@@

\inlinecomment{SCO}{Q: does it make sense to refer forward to FITS support, even though it is 3.0?}
\inlinecomment{BMS}{what about moving it into the future section below?}

@@

TODO: Check when it was added (0.3?). Overview of the supported formats (ASCII,
FITS, votable, HTML, JSViewer/Datatables).

@@

\inlinecomment{SCO}{One subsection per format (if enough new features) ?}
\inlinecomment{BMS}{Do we really need to mention the old version numbers in the list below when a feature was added?}

@@

\inlinecomment{BMS}{Maybe move the command line tools into a separate subsection to highlight them (even though we mostly only have fits related scripts)? They are supposed to be used more frequently by individual users.}
